TIM: Tree Imaging Machine for low-cost digital images of tree cores and cookies

### 2025-04-01 docs/writing/paper.tex
Updated bibliography to besjournals.bst. Figured out the build problems was from the CaptuRING reference. Accented 'A' upset everything
Fixing some bibtex stuff

% Packages
\usepackage[utf8]{inputenc}     
\usepackage{amsmath, amssymb} 
\usepackage{graphicx}          
\usepackage{geometry}           
\usepackage[numbers]{natbib}            
\usepackage{hyperref}          
\usepackage{subcaption}     
\usepackage{multirow}

@@

\section{Introduction} %emw9Mar:  edits throughout to tighten things up... please check I did not add typos or nonsensical stuff. 
Incremental growth rings from trees have provided valuable insights into the abiotic and biotic environment across multiple fields---from climatology to forestry and ecology. Dated tree rings from dendrochronology have been critical to
reconstructing past climates of regional and local environments, providing the most accurate, precise, and reliable dating among alternatives \citep{mann_northern_1999}, and thus fundamnentally informing  our understanding of climate change today \citep{fritts_dendroclimatology_1971} \citep{williams_using_2010} \citep{guibal_dendrochronology_2021} \citep{sheppard_dendroclimatology_2010}. They are also increasingly used in ecology to understand how plant competition affects tree growth in addition to climate \citep{buechling_climate_2017} and have implications in forestry to managing stand dynamics \citep{canham_neighborhood_2004}. These fields have leveraged two basic types of tree sampling techniques to capture the variation of tree rings: cores, which are cylindrical samples collected using an incremental borer, and `cookies,' which are entire cross sections \citep[and thus allow measuring as many radii from the sample as desired,][]{speer_fundamentals_2010}. As understanding tree growth and managing forest becomes more critical to mitigating climate change, scaling up the collection and processing of tree ring samples has become increasingly important.

@@

\bibliographystyle{plainnat}
\bibliography{references}

>>>>

% Packages
\usepackage[utf8]{inputenc}     
\usepackage{amsmath, amssymb} 
\usepackage{graphicx}          
\usepackage{geometry}           
\usepackage{natbib}   
\bibliographystyle{besjournals}

\usepackage{hyperref}          
\usepackage{subcaption}     
\usepackage{multirow}

@@

\section{Introduction} %emw9Mar:  edits throughout to tighten things up... please check I did not add typos or nonsensical stuff. 
Incremental growth rings from trees have provided valuable insights into the abiotic and biotic environment across multiple fields---from climatology to forestry and ecology. Dated tree rings from dendrochronology have been critical to
reconstructing past climates of regional and local environments, providing the most accurate, precise, and reliable dating among alternatives \citep{mann_northern_1999}, and thus fundamnentally informing  our understanding of climate change today \citep{fritts_dendroclimatology_1971,williams_using_2010,guibal_dendrochronology_2021,sheppard_dendroclimatology_2010}. They are also increasingly used in ecology to understand how plant competition affects tree growth in addition to climate \citep{buechling_climate_2017} and have implications in forestry to managing stand dynamics \citep{canham_neighborhood_2004}. These fields have leveraged two basic types of tree sampling techniques to capture the variation of tree rings: cores, which are cylindrical samples collected using an incremental borer, and `cookies,' which are entire cross sections \citep[and thus allow measuring as many radii from the sample as desired,][]{speer_fundamentals_2010}. As understanding tree growth and managing forest becomes more critical to mitigating climate change, scaling up the collection and processing of tree ring samples has become increasingly important.

@@

\bibliography{references}
